---
title: "Revisit Shank2 animal's transcriptomic analysis (Lee et al., 2021)"
author: "KimYG"
date: '2022-07-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(gplots);
library(RColorBrewer)
library(readxl)
library(tidyverse)
```

```{r}
dt.12W.HT <- read_excel(paste(path.expand('~'),"/GitHub/R_script_for_data_analysis/RNA-Sequencing/Shank2/Shank2 RNA-seq result.xlsx", sep = ""), sheet = "12W-HT", range = "A4:P10494")
dt.12W.HM <- read_excel(paste(path.expand('~'),"/GitHub/R_script_for_data_analysis/RNA-Sequencing/Shank2/Shank2 RNA-seq result.xlsx", sep = ""), sheet = "12W-HM", range = "A4:P13294")
#dt.12W.HM[,c(1,3,4,13:16)] <- NULL
head(dt.12W.HT)
head(dt.12W.HM)
```

```{r}
dt.merged.old <- full_join(
                      dt.12W.HT,
                      dt.12W.HM,
                      by = "Mouse symbol",
                      copy = FALSE,
                      suffix = c(".HT", ".HM"),
                      keep = FALSE,
                      na_matches = "na"
                      )
head(dt.merged.old)
```

```{r}
dt.merged.old <- dt.merged.old %>% mutate(HGNC = coalesce(`HGNC symbol.HM`, `HGNC symbol.HT`),
                     EnsembleID = coalesce(`Ensemble ID.HT`, `Ensemble ID.HM`),
                     baseMean = coalesce(baseMean.HT, baseMean.HM),
                     WT1 = coalesce(WT1.HT, WT1.HM),
                     WT2 = coalesce(WT2.HT, WT2.HM),
                     WT3 = coalesce(WT3.HT, WT3.HM),
                     WT4 = coalesce(WT4.HT, WT4.HM),
                     )
#dt.Gene.name <- read.delim("Gene name.txt", header = T, col.names= c("EnsembleID", "Full name", "Species"))
dt.merged <- left_join(dt.merged, 
          #dt.Gene.name, 
          by = "EnsembleID", 
          copy = FALSE,
          suffix = c(".x", ".y"),
          keep = FALSE,
          na_matches = "na"
          )
```


```{r}
dt.stat.old <- dt.merged.old %>% select("HGNC", 
                                "Mouse symbol",
                                #"Full.name",
                                "EnsembleID", 
                                "baseMean", 
                                "log2FC.HT", 
                                "FC.HT", 
                                "p-value.HT", 
                                "adjusted p-value.HT", 
                                "log2FC.HM", 
                                "FC.HM", 
                                "p-value.HM", 
                                "adjusted p-value.HM"
                                )
head(dt.stat.old)
```

```{r}
dt.profile.old <- dt.merged.old %>% select("HGNC", 
                                "Mouse symbol",
                                #"Full.name",
                                "EnsembleID", 
                                "baseMean", 
                                "WT1", 
                                "WT2", 
                                "WT3", 
                                "WT4", 
                                "HT1", 
                                "HT2", 
                                "HT3", 
                                "HT4",
                                "HM1", 
                                "HM2", 
                                "HM3", 
                                "HM4"
                                )
#write.table(dt.profile, file = "12W_merged_profile.txt", na="NA", row.names = F, col.names = T, quote = F, dec = ".", sep = "\t")
#write.table(dt.stat, file = "12W_merged_stat.txt", na="NA", row.names= F, col.names = T, quote = F, dec = ".", sep = "\t")
head(dt.profile.old)
```


```{r}
#save(dt.stat, file = "Shank2.RNAseq.stat.rda")
#save(dt.profile, file = "Shank2.RNAseq.profile.rda")
#load(file = "Shank2.RNAseq.stat.rda")
#load(file = "Shank2.RNAseq.profile.rda")
```

```{r}
DEG.HM.old <- dt.stat.old %>% 
            filter(`adjusted p-value.HM` <= 0.05) %>% 
              select("Mouse symbol")
DEG.HT.old <- dt.stat.old %>% 
            filter(`adjusted p-value.HT` <= 0.05) %>% 
              select("Mouse symbol")
```

```{r}
Old.DEG.HM.profile <-  dt.profile.old %>% 
                  filter(`Mouse symbol` %in% DEG.HM.old$`Mouse symbol`) %>% 
                  select("Mouse symbol", "WT1":"WT4","HM1":"HM4")
#rownames(Old.DEG.HM.profile) <- DEG.HM.old$`Mouse symbol`
head(Old.DEG.HM.profile)
```

```{r}
Old.DEG.HM.stat <-  dt.stat.old %>% 
                  filter(`Mouse symbol` %in% DEG.HM.old$`Mouse symbol`) %>% 
                  select("Mouse symbol", "FC.HM", "adjusted p-value.HM")
#rownames(DEG.HM.profile) <- DEG.HM$`Mouse symbol`
Old.DEG.HM.stat$Class <- rep(1, times = length(DEG.HM.old$`Mouse symbol`))
head(Old.DEG.HM.stat)
```

```{r}
mt.DEG.HM.profile <- as.matrix(DEG.HM.profile)
Map.DEG.HM <- heatmap.2(mt.DEG.HM.profile, 
  Rowv = T, 
  Colv = F,
  na.rm = TRUE,
  dendrogram = "row",
  scale = "row",
  distfun = function(x) dist(x,method = "euclidean"), #"euclidean", "maximum", "manhattan", "canberra", "binary" or "minkowski" 
  hclustfun = function(x) hclust(x,method = "average"), #'ward.D', 'ward.D2', 'single', 'complete', 'average', 'mcquitty', 'median' or 'centroid'
  col = "bluered", 
  srtCol=45,
  symm = TRUE,
  symkey = FALSE,
  symbreaks = TRUE,
  breaks = seq(-3, 3, length.out = 13),
  adjCol=c(1,1), 
  trace = "none",
  main = NA,
  key.title = NA, 
  keysize = 1.2, 
  key.xlab = "Z-score", 
  key.ylab = NA, 
  density.info = "none",
  margins = c(5,5),
  na.color="gray",
  #sepcolor = "black", 
  #sepwidth = c(0.01,0.01), 
  #colsep = c(0:ncol(DEG.HM.profile)),
  #rowsep = c(0,nrow(DEG.HM.profile)),
  )
```


ipa_geneset <- read.table("clipboard", sep = "\t", header = FALSE, stringsAsFactors = FALSE)

splited.list <- list()
for (i in 1:length(ipa_geneset$V1)) {
    splited.list[[i]] <- strsplit(ipa_geneset[i,1], ",") 
}
flatten.list <- unlist(splited.list)
duplicate.list <- flatten.list[duplicated(flatten.list)]
non.duplicate.list <- flatten.list[!flatten.list%in%duplicate.list]
flatten.list <- tolower(flatten.list)

firstup <- function(x) {
   substr(x, 1, 1) <- toupper(substr(x, 1, 1))
x
}

flatten.list <- data.frame(firstup(flatten.list), stringsAsFactors = FALSE)
colnames(flatten.list) <- c("Gene_name")


Synaptic.transmission <- merge(Normalized.value, flatten.list, by = "Gene_name")
Synaptic.transmission2 <- as.matrix(Synaptic.transmission[,-1])
rownames(Synaptic.transmission2) <- Synaptic.transmission$Gene_name
colnames(Synaptic.transmission2) <- colnames(Synaptic.transmission)[-1]
#dataExpr0 <- read.delim("C:/users/KimYG/Desktop/test11.txt",header = TRUE) ### ?ؽ?Ʈ ???? loading, ?????Է?
#rownames = dataExpr0[,1] ### 
#dataExpr0[,1] <- NULL ### delete col #1
#dataMatrix <- data.matrix(dataExpr0)
rc <- rainbow(nrow(Synaptic.transmission2), start = 0, end = 1)
cc <- rainbow(ncol(Synaptic.transmission2), start = 0, end = 1)

###color maping col = colorRampPalette(brewer.pal(9, "RdBu"))(10)


### Heatmap ?׸???
heatmap <- heatmap.2(Synaptic.transmission2, 
  Rowv = T, 
  Colv = F,
  na.rm = TRUE,
  dendrogram = "row",
  scale = "none",
  distfun = dist,
  hclustfun = hclust, 
  col = bluered(19) , 
  srtCol=45,
  symm = TRUE,
  symkey = FALSE,
  symbreaks = TRUE,
  breaks = seq(0.85, 1.15, length.out = 20),
  adjCol=c(1,1), 
  trace = "none",
  main = NA,
  key.title = NA, 
  keysize = 0.5, 
  key.xlab = "Z-score", 
  key.ylab = NA, 
  margins = c(5,5),
  na.color="gray",
  sepcolor = "black", 
  sepwidth = c(0.01,0.01), 
  colsep = c(0:ncol(Imported.data)),
  rowsep = c(0,nrow(ipa_geneset)))

data.pca <- prcomp(Synaptic.transmission2, center = T, scale = T)

print(data.pca)
plot(data.pca, type ="l")
summary(data.pca)

write.csv(Synaptic.transmission2, file = "C:/Users/KimYG/Desktop/DEPs_List.txt", quote = F)


