---
title: "Bar+jitter plot for VOG Baseline data"
author: "Kim YG"
date: "10/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating Bar+Jitter plot using VOG Baseline data

### Loading Packages that we are going to use in this analysis 

**ggplot** and **ggpubr** are used for visualizing our data. **tidyverse** is a specialized package for managing data-set. **Rmisc** is used for calculating descriptive statistics.

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
library(ggpubr)
```

### Import dataset
First, it is necessary to import a dataset from the clipboard. After importing, we will give new column names to the data set and convert two attributes as a factor.   

```{r}
Gain.table <- read.delim("clipboard", header= F)
colnames(Gain.table) <- c("AnimalID", "Gain", "Genotype", "Freq")
Gain.table$Freq <- factor(Gain.table$Freq, levels=c(0.1, 0.25, 0.5, 1.0), order=T)
Gain.table$Genotype <- factor(Gain.table$Genotype, levels=c("WT", "Het"), order=T)
Gain.table$FreqGenotype <- interaction(Gain.table$Freq, Gain.table$Genotype)
head(Gain.table)
```

### Summarize the dataset

```{r}
Gain.table.s <- summarySE(Gain.table, measurevar = "Gain", groupvars = c("Freq", "Genotype"))
Gain.table.s
```

### Generate Bar plot
Stimulus frequency should be converted from numeric value to factor.

```{r}
Gain.table.s2 <- Gain.table.s
Gain.table.s2$Freq <- factor(Gain.table.s$Freq)
Gain.table.s2
```


### Generate simple barplot (mean+sem)
```{r}
bar <- ggplot(Gain.table.s2, aes(x=Freq, y=Gain, fill=Genotype))
bar + geom_bar(stat="identity", 
               position="dodge")+ 
  geom_errorbar(aes(ymin=Gain-se, ymax=Gain+se), 
                width=0.2, 
                position=position_dodge(0.9))
```

### Generate boxplot+dotplot
```{r}
ggplot(aes(y=Gain, x=Freq, fill=Genotype), data=Gain.table)+ 
  geom_boxplot() + 
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               dotsize=.5, 
               position=position_dodge(0.75))
```
### Generate barplot+Jitterplot
```{r}
p <- ggbarplot(Gain.table, 
          x="Freq", 
          y="Gain",
          xlab="Frequency (Hz)",
          ylab="Gain",
          ylim=c(0,1.0),
          width = 0.7,
          add = c("mean_se", "jitter"), 
          color="Genotype",
          palette=c("blue", "red"),
          position = position_dodge(0.8))
```

```{r}
ggplot(Gain.table, 
       aes(x=Freq, y=Gain)) + 
  geom_jitter(aes(color=Genotype),
              position=position_jitter(0.2)) +
  scale_color_manual(values=c("blue", "red"))
```

### Perform hypothesis testing
```{r}
compare_means(Gain~Genotype, group.by="Freq", data=Gain.table, method="t.test")
```
### Add p-values and significance levels
```{r}
p + stat_compare_means(aes(group=Genotype), label="p.signif")
```



























